\pagestyle{empty}
\begin{abstract}
\noindent Since internet has become essential part of people daily life, the requirements for accessing internet in both public and residential area are growing magnificently.Then the new issue about how to share and manager the internet environment in both public and residential area become important to the users. This project will implement a prototype \gls{ios} application as service manager client to work with improved existing Wifi hot-spot system which is provided by \gls{rpi} and remote central management server.
\\ The main idea about this project is to make a system which can provide internet access allocation and internet filtering controls in wireless network. This project is based on previous student master project, that means this project will use same device and resources which used in that master project. To set up existing access control system made by previous master project, most of the references are taken from the master report\cite{TorgeirMR} written by Torgeir Pedersen Cook.
\\ This report will include the improved internet access control system and \gls{ios} administrator application. The improved access control system now will have the function to block the access request device to connect into wireless network for blocking client user purpose. Moreover, the central management server will have better security login mechanism and sending E-mail notification mechanism.The application contains basic administrate access control function like approve access request and block access request from the client user. And also it will have real-time updating access request list and some security communication mechanism.
\\ This prototype has been tested on test \gls{rpi} device and test wireless network environment.
\\ This report will also discuss the usability of this prototype in the commercial market and better improvement on the basic working mechanism of the internet access control system.
\end{abstract}